### 2019-02-01 results.tex
minor

% \textcolor{blue}{Describe what these are in a couple of sentences.}
In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for this Prophet are listed in the table~\ref{tab:prophet_para}. For each cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and $n$ is the number of data points. The application returns the average MSE across cross validations. 
%Using a the model trained by default parameter setting, this average MSE metric is 0.284.

@@

XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
performs both regression and classification. We consider it a regression application and
a classification application in this evaluation.  
Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
Neural network~\cite{ref:neural_network} is a machine learning framework that learns 
and make decisions from patterns in an input dataset. For this application, 
we use a feedforward multilayer perceptron model~\cite{ref:feedforward_nn} 
for the classification task.

@@

\subsection{Empirical Methodology}
To evaluate Seneca, we measure tuning performance, application execution time, and monetary cost.
For tuning performance, we use mean squared error (MSE) for regression tasks 
and percentage accuracy for
classification tasks. The default configuration that we 
consider for each application is described above.
We report results for the default, the best (Seneca's recommendation), 
and the worst performing configurations.  Seneca considers all possible combinations 
of the hyperparameter settings specified in the configuration, uses them
to train, test, and evaluate models for each. 
The default results represents a configuration that a novice or first time 
user might employ when using these applications
as a "black box".  The worst performing scenario shows how bad the results can be
when parameters are poorly tuned.  Finally, the best configuration 
is the one that results from tuning they hyperparameters for the test/train split
that Seneca considers.

>>>>

In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for this Prophet are listed in the table~\ref{tab:prophet_para}. For each cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and $n$ is the number of data points. The application returns the average MSE across cross validations.

@@

XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
performs both regression and classification. We consider it a regression application and
a classification application in this evaluation.  
Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
Neural network~\cite{ref:neural_network} is a machine learning framework that learns 
and make decisions from patterns in an input dataset. For this application, 
we use a feedforward multilayer perceptron model~\cite{ref:feedforward_nn} 
for the classification task. The hyperparameter space and default settings that Seneca uses for these three applications are show in Table~\ref{tab:defaults}.
%Chandra is working on adding this table now, from:
%https://github.com/Heronalps/Seneca/blob/tuning/config/neural_network/config.py
%https://github.com/Heronalps/Seneca/blob/tuning/config/xgboost/config.py
%https://github.com/Heronalps/Seneca/blob/tuning/config/svc/config.py

@@

\subsection{Empirical Methodology}
To evaluate Seneca, we measure tuning performance, application execution time, and monetary cost.
For tuning performance, we use mean squared error (MSE) for regression tasks 
and percentage accuracy for
classification tasks. The default configuration that we 
consider for each application is described above.
We report results for the default, the best (Seneca's recommendation), 
and the worst performing configurations.  Seneca considers all possible combinations 
of the hyperparameter settings specified in the configuration, uses them
to train, test, and evaluate models for each. 
The default results represents a configuration that a novice or first time 
user might employ when using these applications
as a ``black box''.  The worst performing scenario shows how bad the results can be
when parameters are poorly tuned.  Finally, the best configuration 
is the one that results from tuning they hyperparameters for the test/train split
that Seneca considers.
